---
title: "Parallel Computing Prac"
author: "Lara Stipinovich"
format: html
message: false
warning: false
---

```{r}
#| echo: false
library(parallel)
library(foreach)
library(doParallel)
library(knitr)
library(MASS) 
library(iterators)
```

## Question 1:

```{r}
output <- foreach(i = 1:100, .combine = rbind) %do% {
  data <- rexp(100, rate = 1)
  mean_data <- mean(data)
  var_data <- var(data)
  c(Mean = mean_data, Variance = var_data)
}
x <-  head(output)

```

The first 6 means and variances:

```{r}
#| echo: false
x
```

## Question 2:

```{r}
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

runs <- 1000  
size <- 1000

#Finding bootstrap medians for a single sample
boot_medians <- foreach(i = 1:runs, .combine = c, .packages = 'MASS') %dopar% {
    new_data <- sample(galaxies, replace = TRUE)
    median(new_data) 
}
#Run time of single sample
single_par_times <- system.time( 
  boot_medians <- foreach(i = 1:runs, .combine = c, .packages = 'MASS') %dopar% {
    new_data <- sample(galaxies, replace = TRUE)
    median(new_data) 
    }
)
#Run time of serial process
serial_times <- system.time( 
  serial_boot_meds <- replicate(runs, median(sample(galaxies, replace = TRUE)))
)
#Parallel function that batches through 1000 samples
par_bs_batch_fn <- function(runs, size = 1000) {
  num_batches <- runs / size  
  
  unlist(foreach(i = 1:num_batches, .combine = c, .packages = 'MASS') %dopar% {
    replicate(size, median(sample(galaxies, replace = TRUE)))
  })
}

batch_par_times <-  system.time( 
  par_bs_medians_batch <- par_bs_batch_fn(runs, size)
)

stopCluster(cl)

```

Summary of the bootstrap medians from single sample:

```{r}
#| echo: false
summary(boot_medians)
```

Serial Processing Time:

```{r}
#| echo: false
serial_times
```

Parallel (Single Sample) Time:

```{r}
#| echo: false
single_par_times
```

Parallel (Batching 1000 Samples) Time:

```{r}
#| echo: false
batch_par_times
```

## Question 3:

```{r}
cl <- makeCluster(detectCores() - 1)
registerDoParallel(cl)

true_mean <- 1 

coverage_est <- function() {
  #sampling data from exponential with rate = 1
  sample_data <- rexp(50, rate = 1)
  
  #bootstrapping 1000 times over the sampled data
  boot_means <- replicate(1000, mean(sample(sample_data, replace = TRUE)))

  #Finding the lower and upper quantiles for every bootstarp mean
  CI_lower <- quantile(boot_means, 0.025)
  CI_upper <- quantile(boot_means, 0.975)
  #Coverage is where the true mean lies within the CI 
  coverage <- as.numeric(CI_lower <= 1 & CI_upper >= 1)
  return(coverage)
}
#Running the coverage estimation 1000 times
coverage_results <- foreach(i = 1:1000, .combine = c) %dopar% {
  coverage_est()
}

stopCluster(cl)

coverage_probability <- round(mean(coverage_results), 4)

```

Estimated Coverage Probability: `r coverage_probability`

## Question 4:

```{r}
set.seed(1234)

#Function that creates a vector with 5 values and then returning the max value
find_max <- function() {
  it <- irnorm(5) 
  vectors <- as.numeric(nextElem(it, 5))
  return(max(vectors))
}
#Running the function to create 3 vectors and returning the max of each
foreach_result <- foreach(i = 1:3, .combine = c) %do% find_max()

```

The largest values in the vectors:

Vector 1: `r foreach_result[1]`

Vector 2: `r foreach_result[2]`

Vector 3: `r foreach_result[3]`

## Question 5:

```{r}

# Using the foreach function 
system.time({
  foreach_result <- foreach(i = 1:3, .combine = c) %do% find_max()
  print(foreach_result)
})

# Using replicate function
system.time({
  replicate_result <- replicate(3, find_max())
  print(replicate_result)
})


```
